---
title: "Visilization"
author: "Guojg"
date: "2021/12/12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. 参数设置 
```{r}
library(sf)
library(gstat)
library(MASS)

Simulate_mv = function(rowmax, colmax, Sigma, mu, lens) {
  sfc = st_sfc(st_polygon(list(rbind(
    c(0, 0), c(rowmax, 0), c(rowmax, colmax), c(0, 0)
  ))))
  polygon = st_make_grid(sfc, cellsize = c(1, 1))
  
  # sf
  df_poly = as.data.frame(polygon)
  sf_poly = st_as_sf(df_poly)
  
  mv_data = NULL
  nc = c(1:length(mu))
  d = nrow(Sigma)
  set.seed(101125)
  for (i in nc) {
    mv_data = rbind(mv_data,cbind( mvrnorm(n = lens[i], rep(mu[i], d), Sigma), rep(i, lens[i])))
  }
  sf_poly = cbind(sf_poly, mv_data)
  colnames(sf_poly)[6] = 'labels'
  sf_poly
}


```


```{r}
resultdir = "../result/Visilization_EDA/"
```

# 2. 模拟数据1 

```{r}
rowmax = 20
colmax = 20
# Sigma <- diag(rep(1,25))
Sigma <- matrix(rep(0.25,25), ncol = 5)
Sigma[1,1] = 1
Sigma[2,2] = 1
Sigma[3,3] = 1
Sigma[4,4] = 1
Sigma[5,5] = 1
mu = c(-3,0,3)
lens = c(140,120,140)
```

```{r}
library(corrplot)
# corrplot::(Sigma)
```
## 2.1 模拟数据

```{r}
simdata = Simulate_mv(rowmax,colmax,Sigma, mu, lens)
plot(simdata)
```

## 2.2 Visiluation

```{r}
library(mclust)
```

```{r}
class <- simdata$labels
# X = cbind(sf_poly$X1,sf_poly$X2,sf_poly$X3,sf_poly$X4,sf_poly$X5)
table(class)
X = simdata[,1:5]
st_geometry(X) <- NULL
clPairs(X, class)
# head(X)
```


### 2.2.1 PCA

factoextra : Extract and Visualize the Results of Multivariate Data Analyses

```{r}
library(factoextra)
library("FactoMineR")
```

```{r}
res.pca <- PCA(X,  graph = FALSE)
get_eig(res.pca)
```
```{r}
fviz_pca_var(res.pca, col.var = "black")
```
```{r}
fviz_contrib(res.pca, choice = "var", axes = 1, top = 5)

# Contributions of variables to PC2
fviz_contrib(res.pca, choice = "var", axes = 2, top = 5)
```
```{r}

fviz_pca_ind(res.pca,
             label = "none", # hide individual labels
             # habillage = class, # color by groups
             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = FALSE # Concentration ellipses
             ) +  theme_set(theme_bw()) + theme(axis.text = element_text( size = 12))
```

* PC by stats


```{r}
pc <- princomp(X, cor=TRUE, scores=TRUE)
summary(pc)
plot(pc, type="lines")
biplot(pc)
```

### 2.2.2 VAT
```{r}
# NOT RUN {
library(seriation)
library(ggplot2)

x <- as.matrix(X)
dx <- dist(x)
## create regular VAT
# VAT(dx, main = "VAT for Lines", col=NULL)
## ggplot2 version
if (require("ggplot2")) {
  ggVAT(dx) + labs(title = "VAT") + guides(color = guide_legend(override.aes = list(size = 12)))
}


## ggplot2 version
if (require("ggplot2")) {
  ggiVAT(dx) + guides(color = guide_bins())
}

# ## compare with dissplot (shows banded structures and relationship between
# ## center line and the two outer lines)
# dissplot(dx, method = "OLO_single", main = "Dissplot for Lines", col = bluered(100, bias = .5))
# 
# ## compare with optimally reordered heatmap
# hmap(dx, method = "OLO_single", main = "Heatmap for Lines (opt. leaf ordering)",
#   col = bluered(100, bias = .5))
# # }
```

### 2.2.3 SOM

```{r}
library(kohonen)
```

```{r}
gx = ceiling(sqrt(5*sqrt(nrow(X))))
## som
gx = 8
som_x <- som(x, grid = somgrid(gx,gx, "hexagonal"))
summary(som_x)
plot(som_x)
```
```{r}
plot(som_x, type = "mapping", pchs = 19, shape = "round")
```


```{r}
plot(som_x, type = "changes")
```
```{r}
plot(som_x, type = "counts")
plot(som_x, type = "dist.neighbours",palette.name=grey.colors, shape = "straight")
```
This kind of visualisation is also known as a U-matrix plot. Should give you an idea about how to cluster,
since Units near a class boundary can be expected to have higher average distances to their neighbours.
I see 2-3 clusters/districts (keep in mind the grid is toroidal).

```{r}
plot(som_x, type="quality", shape = "straight") #close to 0 = good quality.
```

```{r}
heatmap.som <- function(model){
  for (i in 1:4) {
   plot(model, type = "property", property = getCodes(model)[,i], 
        main = colnames(getCodes(model))[i]) 
  }
}
heatmap.som(som_x)
```

```{r}
library(Umatrix)

um = esomTrain(x,5,5)

plotMatrix(um$Umatrix,um$BestMatches)

```


## 4. MSD

Types of MDS algorithms
There are different types of MDS algorithms, including

Classical multidimensional scaling
Preserves the original distance metric, between points, as well as possible. That is the fitted distances on the MDS map and the original distances are in the same metric. Classic MDS belongs to the so-called metric multidimensional scaling category.

It’s also known as principal coordinates analysis. It’s suitable for quantitative data.

Non-metric multidimensional scaling
It’s also known as ordinal MDS. Here, it’s not the metric of a distance value that is important or meaningful, but its value in relation to the distances between other pairs of objects.

Ordinal MDS constructs fitted distances that are in the same rank order as the original distance. For example, if the distance of apart objects 1 and 5 rank fifth in the original distance data, then they should also rank fifth in the MDS configuration.

It’s suitable for qualitative data.


cmdscale() [stats package]: Compute classical (metric) multidimensional scaling.
isoMDS() [MASS package]: Compute Kruskal’s non-metric multidimensional scaling (one form of non-metric MDS).
sammon() [MASS package]: Compute sammon’s non-linear mapping (one form of non-metric MDS).

All these functions take a distance object as the main argument and k is the desired number of dimensions in the scaled output. By default, they return two dimension solutions, but we can change that through the parameter k which defaults to 2.

```{r}
library(magrittr)
library(dplyr)
library(ggpubr)
mds <- cmdscale(dx)
mds <- data.frame(mds)
colnames(mds) <- c("Dim.1", "Dim.2")
# Plot MDS
ggscatter(mds, x = "Dim.1", y = "Dim.2", 
          size = 1,
          repel = TRUE) + theme_set(theme_bw()) + theme(axis.text = element_text( size = 12))
```
```{r}
clust <- kmeans(x, 3)$cluster %>%
  as.factor()

mds <- mds %>%
  mutate(groups = clust)
# Plot and color by groups
ggscatter(mds, x = "Dim.1", y = "Dim.2",
          color = "groups",
          palette = "jco",
          size = 1, 
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = TRUE)
```
```{r}
clust <- kmeans(mds, 3)$cluster %>%
  as.factor()

mds <- mds %>%
  mutate(groups = clust)
# Plot and color by groups
ggscatter(mds, x = "Dim.1", y = "Dim.2",
          color = "groups",
          palette = "jco",
          size = 1, 
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = TRUE) +   theme(axis.text = element_text(color = "dodgerblue", size = 12),
        axis.text.x = element_text(face = "italic"))
```





# 3. 模拟数据2

## 3.1 模拟数据


```{r}
rowmax = 20
colmax = 20
# Sigma <- diag(rep(1,25))
Sigma2 <- diag(rep(1,5)) 
Sigma2[1,1] = 9
Sigma2[5,5] = 4
mu = c(-3,0,3)
lens = c(140,120,140)
```


```{r}
simdata2 = Simulate_mv(rowmax,colmax,Sigma2, mu, lens)
plot(simdata)
```

## 3.2 Visiluation

```{r}
library(mclust)
```

```{r}
# class <- simdata2$labels
X2 = simdata2[,1:5]
st_geometry(X2) <- NULL
clPairs(X2, simdata2$labels)
# head(X)
```
```{r}
clPairs(X2, simdata2$labels,cex.labels = 2,cex.axis = 2)
```


### 3.2.1 PCA

factoextra : Extract and Visualize the Results of Multivariate Data Analyses

```{r}
library(factoextra)
library("FactoMineR")
```

```{r}
res.pca2 <- PCA(X2,  graph = FALSE)
get_eig(res.pca2)
```
```{r}
fviz_pca_var(res.pca2, col.var = "black")
```
```{r}
fviz_contrib(res.pca2, choice = "var", axes = 1, top = 5)

# Contributions of variables to PC2
fviz_contrib(res.pca2, choice = "var", axes = 2, top = 5)
```
```{r}

fviz_pca_ind(res.pca2,
             label = "none", # hide individual labels
             # habillage = class, # color by groups
             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = FALSE # Concentration ellipses
             ) +  theme_set(theme_bw()) + theme(axis.text = element_text( size = 12))
```


```{r}
pc2 <- princomp(X2, cor=TRUE, scores=TRUE)
summary(pc2)
plot(pc2, type="lines")
biplot(pc2)
```



### 3.2.2 VAT
```{r}
# NOT RUN {
library(seriation)
library(ggplot2)

dx2 <- dist(as.matrix(X2))

ggVAT(dx2) + labs(title = "VAT") + guides(color = guide_legend(override.aes = list(size = 12)))

ggiVAT(dx2) + guides(color = guide_bins())

```

### 3.2.3 SOM

```{r}
library(kohonen)
```

```{r}
x2 = as.matrix(X2)
gx2 = ceiling(sqrt(5*sqrt(nrow(X2))))
som_x2 <- som(x2, grid = somgrid(gx2,gx2, "hexagonal"))
summary(som_x2)
plot(som_x2)

```
```{r}
plot(som_x2, type = "mapping", pchs = 19, shape = "round")
```


```{r}
plot(som_x2, type = "changes")
```
```{r}
plot(som_x2, type = "counts")
plot(som_x2, type = "dist.neighbours",palette.name=grey.colors, shape = "straight")
```
This kind of visualisation is also known as a U-matrix plot. Should give you an idea about how to cluster,
since Units near a class boundary can be expected to have higher average distances to their neighbours.
I see 2-3 clusters/districts (keep in mind the grid is toroidal).

```{r}
plot(som_x2, type="quality", shape = "straight") #close to 0 = good quality.
```

```{r}
# heatmap.som <- function(model){
#   for (i in 1:4) {
#    plot(model, type = "property", property = getCodes(model)[,i], 
#         main = colnames(getCodes(model))[i]) 
#   }
# }
heatmap.som(som_x2)
```

```{r}
library(Umatrix)

um2 = esomTrain(x2,5,5)

plotMatrix(um2$Umatrix,um2$BestMatches)

```


### 3.2.4. MSD


```{r}
library(magrittr)
library(dplyr)
library(ggpubr)
mds2 <- cmdscale(dx2)
mds2 <- data.frame(mds2)
colnames(mds2) <- c("Dim.1", "Dim.2")
# Plot MDS
ggscatter(mds2, x = "Dim.1", y = "Dim.2", 
          size = 1,
          repel = TRUE)
```
```{r}
clust <- kmeans(x2, 3)$cluster %>%
  as.factor()

mds2 <- mds2%>%
  mutate(groups = clust)
# Plot and color by groups
ggscatter(mds2, x = "Dim.1", y = "Dim.2",
          color = "groups",
          palette = "jco",
          size = 1, 
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = TRUE)
```
```{r}
clust <- kmeans(mds2, 3)$cluster %>%
  as.factor()

mds2 <- mds2 %>%
  mutate(groups = clust)
# Plot and color by groups
ggscatter(mds2, x = "Dim.1", y = "Dim.2",
          color = "groups",
          palette = "jco",
          size = 1, 
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = TRUE) +   theme(axis.text = element_text(color = "dodgerblue", size = 12),
        axis.text.x = element_text(face = "italic"))
```
## 3.3 Save figure to pdf
```{r}
#specify path to save PDF to
destination = paste0(resultdir, 'mv_simate_vis_cor_0.pdf')
#open PDF
pdf(file = destination)

#specify to save plots in 2x2 grid
par(mfrow = c(2, 2))

#save plots to PDF
# for (i in 1:4) {
# simualte data
clPairs(X2,
        simdata2$labels,
        cex.labels = 2,
        cex.axis = 2)
# PCA
fviz_pca_ind(
  res.pca2,
  label = "none",
  # hide individual labels
  # habillage = class, # color by groups
  palette = c("#00AFBB", "#E7B800", "#FC4E07"),
  addEllipses = FALSE # Concentration ellipses
) +  theme_set(theme_bw()) + theme(axis.text = element_text(size = 12))
# VAT
ggiVAT(dx2)
# SOM
plot(som_x2,
     type = "dist.neighbours",
     palette.name = grey.colors,
     shape = "straight")
# }

#turn off PDF plotting
dev.off() 
```

```{r}
library(gridExtra)
figls = list()
# figls[[1]] = clPairs(X2,
#         simdata2$labels,
#         cex.labels = 2,
#         cex.axis = 2)
figls[[1]] = fviz_pca_ind(
  res.pca2,
  label = "none",
  # hide individual labels
  # habillage = class, # color by groups
  palette = c("#00AFBB", "#E7B800", "#FC4E07"),
  addEllipses = FALSE # Concentration ellipses
) +  theme_set(theme_bw()) + theme(axis.text = element_text(size = 12))
figls[[2]] = ggiVAT(dx2)
# ggplot2::ggsave(figls)

# library(gridExtra)

pdf("plots.pdf", onefile = TRUE)
for (i in seq(length(figls))) {
  do.call("grid.arrange", figls[[i]])  
}
dev.off()

```
```{r}
pdf("plots.pdf",width = 4, height=4)
ggiVAT(dx2)
dev.off()
```

